SVG: The Paper

### 2022-04-13 Analysis/index.Rmd
Update index.Rmd

---
title: 'SVG: The Paper'
author: "Alasdair and Anna"
date: "11/04/2022"
output:
  tufte::tufte_html:
    toc: TRUE
    number_sections: true
---

@@

```{r, fig.cap = "Accuracy of our model appears to vary with the strength of an individual's proximity bias."}
# computed in xxxx.R
fit <- readRDS("scratch/qjep_model_fit.rda") %>%
  full_join(a_acc, by = c("observer", "condition"))

>>>>

---
title: 'SVG: The Paper'
author: "Alasdair Clarke, Amelia Hunt &  Anna Hughes"
date: "13/04/2022"
output:
  tufte::tufte_html:
    toc: TRUE
    number_sections: true
---

@@

```{r, fig.cap = "Accuracy of our model varies with the strength of an individual's proximity bias."}
# computed in xxxx.R
fit <- readRDS("scratch/qjep_model_fit.rda") %>%
  full_join(a_acc, by = c("observer", "condition"))
